The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-01-09 paper/ms.tex
Section 3.3 revised

\begin{figure}
  \includegraphics[width=0.45\textwidth]{Neufeld.png}
 \caption{Escape fraction as a function of the
   product $(a\tau_{\rm H})^{1/3}\tau_{a}$. The analytic solution for
   the infinite slab is shown as a continuous line. Different dashed
   lines correspond to different rotational velocities.
   \label{fig:efvsNeufeld}}   
\end{figure}

@@

In Figure \ref{fig:efvsNeufeld} we put these results in the context of
the analytic solution for the infinite slab \citep{Neufeld90}. In
Neufeld's set-up the analytic solution depends uniquely on the product
$(a\tau_{\rm   H})^{1/3}\tau_{a}$, an approximation that is valid only
in the limits where $a\tau_{\rm   H}\gg 1$. The dashed lines in Figure
\ref{fig:efvsNeufeld} correspond to the cases of different
velocities. First of all we note that the escape fraction does not
increase from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, this is
explained since we are in a regime where the condition for the
analytic expectations  ($a\tau_{h}\gg 1$) does not hold. This figure
also shows that the escape fraction is higher by factors of $2-10$
than the expectation for a slab with centrally distributed
sources. Furthermore, the decrease of the escape fraction with
increasing optical depth is also slower.

>>>>

\begin{figure}
  \includegraphics[width=0.45\textwidth]{Neufeld.png}
 \caption{Escape fraction as a function of the
   product $(a\tau_{\rm H})^{1/3}\tau_{a}$. The analytic solution for
   the infinite slab is shown as a continuous line. Different dashed
   lines correspond to different rotational velocities, for this models 
   $\tau_a = 1$.
   \label{fig:efvsNeufeld}}   
\end{figure}

@@

In Figure \ref{fig:efvsNeufeld} we put these results in the context of
the analytic solution for the infinite slab \citep{Neufeld90}. In
Neufeld's set-up the analytic solution depends uniquely on the product
$(a\tau_{\rm   H})^{1/3}\tau_{a}$, an approximation that is valid only
in the limits where $a\tau_{\rm   H}\gg 1$. The dashed lines in Figure
\ref{fig:efvsNeufeld} correspond to the cases of different
velocities. First of all we note that the escape fraction does not
increase from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, this is
explained since there is a transition from a opaque to an extremely opaque medium
which affect affects how \ly photons scape from the medium: single flight 
vs single excursion.
 %we are in a regime where the condition for the analytic expectations  ($a\tau_{h}\gg 1$) does not hold. 
This figure also shows that the escape fraction is higher by factors of $2-10$
than the expectation for a slab with centrally distributed
sources. Furthermore, the decrease of the escape fraction with
increasing optical depth is also slower.

transition from the opaque to
  extremely opaque medium, which affects how Lya photons escape from
  the medium: single flight vs single excursion
